Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-01-18 parallel.tex
Updated.

@@

The performance of \enzo\ has been extensively studied using the
software package LCAPerf.  More on LCAPerf can be found in section
\ref{sec.performance}

@@

\red{
This is really James' section.  Profiling the code is very difficult because
of the many possible configurations that it can be run under.  In general,
we want to show both AMR and unigrid calculations scale, for cosmology runs
and for pure hydro (i.e. turbulence) runs.  The gravity scales far differently
than the hydro, so perhaps we should do a gravity-only (dark matter?) vs. 
hydro only (driven isothermal turbulence, non-gravitating) scaling?
We should also include performance information for some of the very large
simulations that we've done -- 2048$^3$ unigrid and 512$^3$ AMR runs.
}

\red{It seems like this section will be fiercely debated.  So have fun.}

>>>>

% GB to work on this
%  - expand to include better description
%  - include load balancing options

@@

@@

\subsubsection{Performance model \red{(Greg)}}

% Maybe include Greg's text on general scaling arguments

\subsubsection{Unigrid scaling \red{(Brian)}}

% Brian to work on this, scaling data from Harkness

\subsubsection{AMR scaling \red{(Greg)}}

% Greg to work on this, scaling data from his runs, or maybe from John Wise
